% Guidance - 2 pages
% Details of your team's testing strategy, and the results, including how well
% the solution met the requirements. Your evaluation should include a specific
% section relating to a professional/social/ethical/environmental aspect of
% your system solution.
\section{Description of the Team's Testing Strategy}

Throughout the duration of the project, my group was thorough and rigorous in our 
continual testing of the device through a variety of means. Through use of the 
version control software, git, new features were added as branches to the main
project. This enabled new features to be tested externally to the main body of 
the project, and furthermore enabled strict code reviews to be performed on each 
contribution to the group solution. 
In addition, a debugging library was implemented, allowing messages to be 
output for debugging purposes only, and easily removed from the solution. 
Furthermore, the group solution underwent extended testing and was continually 
running in the laborotories throughout the duration of the project. 

\subsection*{Individual Testing}

As our team used the version control system, git, we were able to produce new 
branches of the project for each new feature. 
This not only enabled each new features to be tested separately, but enabled 
different group members to work on alternate features simultaneously, with no 
possibility of interference. 
After the completion of a new feature, prior to the inclusion within the group 
solution, each section of the feature underwent individual tests. 
For a greater ease in testing the project,  a debugging library was created, 
enabling serial messages to print diagnostics. 
The debugging library was only included in the 
binaries installed on the device if the make command included it. This 
means, for the purposes of testing it was possible to use \texttt{make debug} 
and have messages containing text, or values printed out over serial. 
However, once sufficient testing was done, no 
alterations had to be made to the code to remove these statements, and 
instead the project could be installed by calling \texttt{make}. 
This therefore provided a simplistic tool, effectively creating two distinct 
modes of operation: a debugging mode, where information was output over serial, 
and a production mode, where normal operation ensued. 

\subsection*{Code Review}

Before each contribution was incorporated into the group's solution, it was 
first checked over by at least two other group members to ensure the quality of 
the solution was high. These checks often resulted in re-factoring code to 
achieve a more streamlined end product, examples of which could include the 
simplification of logic for writing text to the LCD display through pointer 
arithmetic, or simplifying code within an interrupt handler in order to avoid 
race conditions. 

\subsection*{Integration Testing}

Following the combination of individual components into the group solution, the 
combined product was then tested thoroughly to ensure no erroneous behaviour 
could occur. This was primarily done by leaving the solution running for long 
periods of time within the labs, and continually checking to ensure nothing unexpected 
had occurred at any point.
In addition, each new addition to the solution was fully tested by each group 
member on its incorporation within the project. 

\section{Results of Testing Strategy and How Well This Met the Requirements}

The groups testing strategy proved very efficient as capable. Through the use 
of individual branches for new features, any issues caused by new additions would 
not affect other parts of the group solution, and enabled a much simpler debugging 
process.  
Through the testing strategy many different issues were identified, and dealt 
with without before becoming significant probelm. 
At many points throughout the project minor issues were discovered and corrected 
by the groups testing strategy. 

Through leaving the group solution running for long periods of time, a continual 
testing strategy explored a large number of test cases and different situations.

Furthermore, a careful eye was kept at all times to ensure that the product's
functionality was as desired, and further testing was done to ensure the 
requirements of the specification were fully met.
Through our thorough and rigorous testing, the end product was remarkably stable. 
We encountered no situations that would cause the product to produce undesirable 
behaviour, and furthermore the full requirements were met.

\section{A Social/Ethical Aspect of the Group Solution} 

The group solution created has the potential to solve any issues that may arise 
when considering the usability of the user interface with respect to a disabled 
user or users. Interaction with the device via the 16 digit keypad that is on 
the host board may not provide a very effective method of interaction with the 
device for many users. However, the shell style interface allows user to interact 
with the device via a computer. Interaction with a computer, and hence the MBED 
would typically be achieved through use of a keyboard, however, there are many 
alternative methods of input that would allow interaction with the MBED board in 
a method better suited for a disabled user. These input methods could include 
tools such as an improved computer keyboard, speech recognition, or the tailoring 
of custom tools to allow a greater level of interaction. Such tools are 
highlighted in many works, examples of which could include \textit{Computer Access for People with 
Disabilities: A Human Factors Approach}, or \textit{Universal Access in 
Human-Computer Interaction} \cite{disabled-book, disabled-book2}. The flexibility of 
input method provides a wide range of possible tools enabling communication with 
the device. This therefore avoids significantly the problem of interaction for 
a handicapped or disabled user. 
